### 2016-03-10 manuscript.Rnw
[fix #13] clarify diff betwwen vignette and appendix

The package vignettes provide two demonstrations of the integration of a
phylogeny and data associated with the taxa it represents. Specifically, the ``Data
mashups'' vignette provides an example of how data associated with tip-taxa can
be gathered and visualized. Another vignette titled ``meta-analysis''
demonstrates how a complete analysis, including the gathering of data and a
phylogeny, can be performed in a single R session. We further demonstrate the
integration of phylogenetic data retrieved using \texttt{rotl} with other data
here.

>>>>

Here we show how we can obtain a map of the occurrences for a subset of the cat
species (genus \textit{Lynx}) that were included in the phylogeny retrieved from
the Felidae study above. We extract the species names from the phylogeny, and use
them to ask for the records for these species found in GBIF
(Figure~\ref{fig:cat_map}). We include the code to reproduce this figure in the
Appendix.

In addition of an introduction on how to use the package, \texttt{rotl} includes
two vignettes that demonstrate how to integrate a phylogeny and data associated
with the taxa it represents. Specifically, the ``Data mashups'' vignette
provides an example of how to retrieve a phylogeny for species a researcher may
have data for, and visualize both the phylogeny and data associated with the
species at the tips. The other vignette titled ``Meta-analysis'' demonstrates how a complete
comparative method analysis, including the gathering of data and a phylogeny, can be
performed in a single R session. We reproduce a published meta-analysis testing
for differential investment in male and female offsprings among 51 species of
birds. As new versions of the OTL API and \texttt{rotl} are released,
these vignettes will be kept up-to-date.
